Data Management for LSST Special Programs

### 2024-03-27 sec_sci.tex
add caveats to SProc

\textbf{Necessary -- } When the primary science goal for a Special Program 
cannot be met by including the data in standard processing (e.g., Prompt processing),
or where doing so would compromise the Main Survey data products (e.g., introduce additional non-uniformity beyond what would be expected based on the survey strategy).

@@

The definitions of possible and necessary are further illustrated with examples in Section~\ref{ssec:proc_special}.
Note that secondary science goals may be considered as ``not necessary".

The general scope of Special Processing, including situations in which cross-match and table joins 
would be possible and scientifically relevant, 
are ultimately left to the discretion of Rubin Data Management in Operations.

Further discussion on Special Processing, with examples, is provided in Section~\ref{ssec:proc_special}.

>>>>

\textbf{Necessary -- } When the \emph{primary} science goal for a Special Program 
cannot be met by including the data in standard processing (e.g., Prompt processing),
or where doing so would compromise the Main Survey data products (e.g., introduce additional
non-uniformity beyond what would be expected based on the survey strategy).

@@

\textbf{Caveat I. The scope} of Special Processing is at the discretion of
Rubin Data Management, including the timelines for data releases.

\textbf{Caveat II. The definition of possible} comes from the requirement referenced
for the first motivation in the list above (i.e., is not defined by this document).
However, this definition failed to recognize cost-benefit tradeoffs to implementing
and operating Special Processing, and does not account for the costs of operating,
documenting, and maintaining additional processing campaigns and their data products.
Furthermore, the science goals and complexity of Special Programs might evolve
significantly over the 10 year survey.
Even in situations that require no algorithmic or software development,
the Rubin DM team might not have the staffing to handle Special Processing
for all cases that are technically "possible".

\textbf{Caveat III. The definition of necessary} is defined here in this document only.
We emphasize that the term applies only to the \emph{primary} science goals, and does
not cover secondary or "bespoke" science goals for a Special Program.
Users should anticipate that User-Generated Processing will be needed for these cases.

The definitions of possible and necessary are further illustrated with examples in Section~\ref{ssec:proc_special}.
